---
title: "Series index"
date: "`r Sys.Date()`"
description: Catalog metadata for Banco de España time series, including stable sequential numbers and API series codes.
toc: true
tbl-cap-location: bottom
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
    warning: false
    message: false
    tidy: "styler"
    dev: "ragg_png"
    dpi: 300
    out.width: "100%"
---

This article lists time series available in Banco de España catalog metadata.
Last updated: **`r format(Sys.Date(), "%d-%B-%Y")`**.

Use the stable sequential number (`Numero_secuencial`) to load a time series
from bulk CSV files, as shown in the example. Use `Nombre_de_la_serie` as the
API series code for the Statistics web service (API) functions.

## Summary

```{r}
#| label: reactable
#| echo: false
library(tidyBdE)
library(ggplot2)
library(dplyr)
library(tidyr)

series <- bde_catalog_load()

# Clean the data.
series_clean <- series |>
  filter(!is.na(Numero_secuencial)) |>
  select(
    Numero_secuencial,
    Descripcion_de_la_serie,
    Titulo_de_la_serie,
    Tipo_de_variable,
    Fecha_de_la_primera_observacion,
    Fecha_de_la_ultima_observacion,
    Frecuencia_de_la_serie,
    Fuente
  ) |>
  as_tibble()

library(reactable)

reactable(
  series_clean,
  filterable = TRUE,
  searchable = TRUE,
  resizable = TRUE,
  showPageSizeOptions = TRUE,
  striped = TRUE,
  defaultColDef = colDef(
    minWidth = 200,
    html = TRUE,
    align = "left",
    vAlign = "center"
  ),
  paginationType = "jump",
  defaultPageSize = 5,
  compact = TRUE,
  elementId = "bde-series"
)
```

## Example {#example}

The following workflow searches for and retrieves a specific time series.

```{r}
#| label: tbl-example
#| tbl-cap: "Search results"
library(tidyBdE)
library(tidyverse)

# Search for French GDP.
fr <- bde_catalog_search("Francia(.*)PIB")

# Display the table in the vignette.
fr |>
  select(Numero_secuencial, Descripcion_de_la_serie) |>
  knitr::kable()
```

```{r}
#| label: tbl-meta
#| tbl-cap: Metadata of the indicator
# Extract the first matching time series.
fr |>
  # Select the stable sequential number.
  select(Numero_secuencial) |>
  # Select the first record.
  slice(1) |>
  # Convert to numeric.
  as.double() |>
  # Load the time series.
  bde_series_load()

# Show the series metadata.
fr |>
  # Select the stable sequential number.
  select(Numero_secuencial) |>
  # Select the first record.
  slice(1) |>
  # Convert to numeric.
  as.double() |>
  # Load the series metadata.
  bde_series_load(extract_metadata = TRUE) |>
  # Display the table in the vignette.
  knitr::kable()
```
